%!TEX root = main.tex

\section{Introduction}
% no \IEEEPARstart

% Internet consumers now care more about ``what" they can get from network. However TCP/IP, the network architecture of Internet, is initially designed based on the principle of ``where" to connect the users. This mismatch between the user-demand and network-principle makes the network difficult to satisfy the users. To overcome this, some clean-state network architectures have been proposed. NDN is one of such clean-state architecture\cite{NDN}. In NDN, consumers just send Interest into the network, and the network will return the corresponding Data to it. The consumers are unnecessary to care about where to get the Data.

% As the NDN network layer is based on best-effort transmit model, congestion and dropping packets are still possible. Transport control is still necessary to guarantee effective transfer. Some TCP-style transport control mechanisms have been proposed for NDN, such ICP\cite{ICP}, CCTCP\cite{CCTCP} and HR-ICP\cite{shape}. However these TCP-style transport mechanisms in NDN still have the same problems as TCP/IP, such as low link utilization and high packets dropping rate. Explicit Congestion Notification(ECN) is a promise way to achieve high link utilization\cite{XCP} . Adaptive forwarding is a new feature of the NDN\cite{Adaptive}. Adaptive forwarding let router choose a suitable path according the network situation. If the router senses the link has been congested, then it can choose another path. It is completely different with TCP/IP. In TCP/IP the forwarding process is strictly followed the route table. By the adaptive forwarding, router can deal with the network congestion quickly.

% But by now, as what we have known, no ECN-style congestion mechanism has been proposed in NDN and there is little research about the congestion avoiding mechanism making use of the adaptive forwarding. In this paper we use the Data(which comes back along the same path with Interest) to carry the ECN information, and design an ECN transport mechanism for NDN. We also make use of the SDN's network-wide information to design a smart forwarding mechanism. Joining the ECN and smart forwarding mechanism, we can not only improve single link bandwidth utilization but also the whole network resource utilization. Summary, our main contributions are:

% \begin{enumerate}
% \item[1.] First achieve an ECN transport mechanism in NDN.
% \item[2.] First use SDN-style control information to design smart forwarding mechanism to ultimately use the whole network resource.
% \item[3.] Packet-level simulation shows that joining ECN and smart forwarding in NDN can improve link utilization and total flow complete time.
% \end{enumerate}

Internet consumers typically care more about \emph{what} information they want, instead of \emph{where} it is located. However, the Internet architecture is initially designed for point-to-point communication. This mismatch between user demand and network infrastructure makes Internet applications struggling with the gap between where and what. Several clean slate network architectures have been proposed to address this problem. Among those proposals, NDN\cite{NDN} assigns each data a unique name for addressing and caching, which is compatible with Internet demand and exhilarate information dissemination greatly. 

As NDN adopts simple best-effort packet transport between neighboring NDN nodes, congestion might occur and packets could be dropped due to congestion. Therefore transport control is essential for effective and efficient data transmission. Some TCP-style transport control mechanisms in NDN have been proposed, such as ICP\cite{ICP}, CCTCP\cite{CCTCP} and HR-ICP\cite{shape}. These TCP-style proposals still suffer from the same problems as that in TCP, e.g. low link utilization, high packet dropping rate. Explicit Congestion Notification (ECN) is a promising technique to achieve high link utilization\cite{XCP}. Adaptive forwarding\cite{Adaptive} in NDN is proposed which lets router adaptively select forwarding interface among the multiple available ones according to network condition. Different from TCP/IP in which forwarding interfaces are determined statically, adaptive forwarding could react to congested links and bypass them quickly.

As far as we know, there's still no ECN-style congestion mechanism proposed for NDN and little research about congestion avoidance mechanism by utilizing adaptive forwarding has been investigated. In this paper, by utilizing the feature in NDN that there's one-to-one mapping of Interest-Data and Data is forwarded back along exactly the path Interest is transmitted, we \red{add} an ECN field in Data packet, which contains ECN information to notify consumer or down-stream routers to adapt their transmission rate. What's more, we also exploit the power of network-scale information by SDN\cite{SDN} to design a smart \red{forwarding} mechanism. By combining ECN and smart forwarding mechanism, we could not only improve bandwidth utilization on single links but also the resource utilization in the whole network. In summary, our main contribution are:

\begin{enumerate}
	\item[1.] We first propose an ECN-based transport mechanism in NDN.
	\item[2.] We are the first to utilize SDN technique to design smart forwarding mechanism to fully exploit the resource in the whole network.
	\item[3.] Packet-level simulation shows that joint ECN and smart forwarding in NDN could improve link utilization and total Flow Complete Time (FCT).
\end{enumerate}

The rest of the paper is organized as followed: Sec. \ref{sec:related} discusses related works. In Sec. \ref{sec:bg} we introduce the NDN's feature which we utilize to design our transport mechanism. In Sec. \ref{sec:rationale} we discuss the design rationale. Sec. \ref{sec:design} introduces the ECN congestion mechanism and the smart forwarding. In Sec. \ref{sec:simulation}, we demonstrate the effectiveness of our mechanism. Finally Sec. \ref{sec:conclude} concludes the paper.
